\section{Data Set Card: Future Statements}
\\
\\
\textbf{Data Set Description}
\\
\\
This Data Set Card originates from \url{https://huggingface.co/datasets/fidsinn/future-statements}
The english language data set contains 2,500 statements.
50\% of the relate to future events and 50\% of which relate to non-future events.
The statements were collected manually and programmatically from several websites and datasets.
The labels were set manually or programmatically (including corresponding manual examination of the labels).
\\
\\
\textbf{Dat Set Motivation}
\\
\\
The sole purpose of this dataset was to fine tune the distilbert-base-uncased \url{https://huggingface.co/distilbert-base-uncased} model into our distilbert-base-future \url{https://huggingface.co/fidsinn/distilbert-base-future} model.
The dataset was created by students from the University of Leipzig in the Big Data and Language Technologies Module of the Webis Group \url{https://huggingface.co/webis}.
\\
\\
\textbf{Data Set Composition}
\\
\\
The instances are represented by single-/ or multi-sentence statements from following sources (unequally distributed):
%
\begin{itemize}
    \item \url{http://www.kaggle.com/unitednations/un-general-debates}
    \item \url{http://data.world/ian/united-nations-general-debate-corpus}
    \item \url{http://gadebate.un.org/}
    \item \url{http://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/0TJX8Y}
    \item \url{http://www.wsj.com/}
    \item \url{http://www.vox.com/}
    \item \url{http://futechblog.com/}
    \item \url{http://www.weforum.org/}
    \item \url{http://wired.com/}
    \item \url{http://openai.com/blog/}
    \item \url{http://techcrunch.com/}
    \item \url{http://futurism.com}
\end{itemize}
%
- The dataset consists of 2,500 statements in total, 50\% of which relate to future events and 50\% of which relate to non-future events.
\\
\\
\textbf{Data Set Annotation}
%The label is represented by the 'future'-column:
\begin{itemize}
    \item 0: No future statement
    \item 1: future statement
\end{itemize}%
\\
\\
\textbf{Noise, Biases and Redundancies}
\\
\\
The main goal of the data collection process was to find future statements and general statements in equal amount.
The thematic content within the statements can be redundant and some topics can be much more present.
The dataset was not created to work with the thematic content while only fine-tune an already existing model into a model which is sensible for future and non-future statements.
Data in the 'statement'-column is publicly available and does not contain confidential information.
It was collected in the months 06/2022-07/2022 but the content of the dataset is independent of the data collection period and can be from earlier periods.
\\
\\
\textbf{Data Set Collection Process}
\\
\\
The data is directly observable on the websites mentioned in upper section.
It was collected manually and programmatically (using Pythons NLTK library for automatic sentence-extraction and Regex-filtering)
from graduate students D. Baradari \url{https://huggingface.co/Dunya}, F. Bartels \url{https://huggingface.co/fidsinn}, A. Dewald, J. Peters \url{https://huggingface.co/jpeters92} as part of a data science module of the University of Leipzig.
The data was obtained in the months 06/2022-07/2022 but the content of the dataset is independent of the data collection period and can be from earlier periods.
\\
\\
\textbf{Dataset Maintenance}
\\
\\
Curators of the dataset can be contacted via the Huggingface community tab \url{https://huggingface.co/datasets/fidsinn/future-statements/discussions}.

It is not planned to update the dataset for further work or investigations.